Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2024-04-29 manuscript.qmd
adding three chunks in order to check in which conditions xgboost predicted a positive efficacy for the reduction strategies.

```{r}
library ("ggplot2") # version 3.4.4
library ("gridExtra") # version 2.3
library ("dplyr") # version 1.1.2      
library ("paletteer") # version 1.4.0
library ("tibble") # version 3.2.1
library ("tidyr") # version 1.3.0
library ("ALFAM2") # version 3.7
library ("randomForest") # version 4.7.1.1
library ("xgboost") # version 1.7.6.1
library ("glmnet") # version 4.1.8
library ("shapviz") # version 0.9.3
library ("treeshap") # version 0.3.1
```

@@

>>>>

```{r}
library ("ggplot2") # version 3.4.4
library ("gridExtra") # version 2.3
library ("dplyr") # version 1.1.2      
library ("paletteer") # version 1.4.0
library ("tibble") # version 3.2.1
library ("tidyr") # version 1.3.0
library ("ALFAM2") # version 3.7
library ("randomForest") # version 4.7.1.1
library ("xgboost") # version 1.7.6.1
library ("glmnet") # version 4.1.8
library ("shapviz") # version 0.9.3
library ("treeshap") # version 0.3.1
library ("kableExtra") # version 1.3.4
```

@@

```{r}
data_scenarios %>%
    filter (efficacy_xgboost > 0) %>%
    select (efficacy_xgboost, tan.app, app.mthd, app.rate, man.source, incorp, group_temp, group_wind, group_rain) %>%
    kable ()
```

```{r}
data_scenarios %>%
    filter (efficacy_xgboost > 0) %>%
    select (tan.app, app.mthd, app.rate, man.source, incorp, group_temp, group_wind, group_rain) %>%
    lapply (table)
```

```{r, fig.width = 10, fig.height = 5}
data_scenarios %>%
  filter (efficacy_xgboost > 0) %>%
  select (efficacy_xgboost, tan.app, app.mthd, app.rate, man.source, incorp, group_temp, group_wind, group_rain) %>%
  ggplot () +
    geom_histogram (aes (efficacy_xgboost)) +
    facet_wrap (~ tan.app + app.rate)
```
